### 2021-08-12 paper/paper.tex
Remove last statement from conclusions since it is not substantiated in the main part of the paper
Apply suggestions from code review
Thanks for the suggestions, @ranocha!

Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.57 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
looks as follows:

@@

While our Julia code is faster than the established HPC Fortran code FLUXO for this non-trivial
example, we do not claim that Julia is generally faster than Fortran, C, or C++.
Instead, we would like to emphasize that Julia code can be \emph{at least
as fast} as code written in these traditional scientific computing languages.
Further, we expect to be able to achieve similar performance with either language, and that
remaining performance differences are due to how much time and effort has been spent to optimize
each code.  \trixi owes its performance optimizations in part to the code introspection and
profiling tools available in Julia. Similar tools used to optimize the performance in other
languages are often not as easy to use as their Julia counterparts.

@@

While Julia offers its own approach to distributed computing via the \lstinline{Distributed} package
in the standard library, its performance and scalability are currently limited \cite{byrne2021mpi}.
As an alternatively, the package MPI.jl utilizes the Message Passing Interface (MPI) for data
exchange \cite{byrne2021mpi}. It provides an API similar to MPI's C interface and allows to either
wrap MPI binaries installed through Julia's package manager or to make use of an existing MPI
installation.  Most Julia projects focusing on distributed-memory simulations seem to be using
MPI.jl, such as ClimateMachine.jl\footnote{\url{https://github.com/CliMA/ClimateMachine.jl}} or
ImplicitGlobalGrid.jl\footnote{\url{https://github.com/eth-cscs/ImplicitGlobalGrid.jl}}.  In
general, the performance of MPI programs written in Julia is to be comparable to C programs
\cite{hunold2020benchmarking}, and parallel simulations with Julia have been shown to scale
to more than 5,000 GPUs with MPI.jl \cite{omlin2020solving}.

@@

Even though the aforementioned difficulties do not prevent massively parallel simulations with
Julia, they raise the entry barrier for new users and developers. The overarching issue, however, is
that at the time of writing, there is little precedence in terms of openly available tutorials,
citable publications, or highly scalable example applications that can be used to learn about best
practices for MPI-based parallism in Julia. Thus while in general it is justified to be cautiously
optimistic that most issues can be overcome, it is too early to make a final assessment on the
suitability of Julia for highly parallel simulations.

@@

Learning a new programming language naturally requires some time and effort.
In our experience, however, it has paid off and we do not want to miss the
many useful features of \trixi enabled by Julia and its ecosystem. While there is
no need to switch to Julia if people are satisfied with their existing
tools, we encourage researchers to try out Julia for scientific computing and to stay for a while.
The Julia
community (on the Julia Discourse forum\footnote{\url{https://discourse.julialang.org}}
or Slack/Zulip workspaces) is usually welcoming and helpful, both for new and
experienced users. Making use of existing learning material and asking questions
appears to be important since a new programming style is necessary to make full
use of all of Julia's strengths.

>>>>

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
looks as follows:

@@

While our Julia code is faster than the established HPC Fortran code FLUXO for this non-trivial
example, we do not claim that Julia is generally faster than Fortran, C, or C++.
Instead, we would like to emphasize that Julia code can be \emph{at least
as fast} as code written in these traditional scientific computing languages.
Further, we expect to be able to achieve similar performance with either language
by spending enough time and effort to optimize the respective code.
\trixi owes its performance optimizations in part to the code introspection and
profiling tools available in Julia. Similar tools used to optimize the performance in other
languages are often not as easy to use as their Julia counterparts.

@@

While Julia offers its own approach to distributed computing via the \lstinline{Distributed} package
in the standard library, its performance and scalability are currently limited \cite{byrne2021mpi}.
As an alternatively, the package MPI.jl utilizes the Message Passing Interface (MPI) for data
exchange \cite{byrne2021mpi}. It provides an API similar to MPI's C interface and allows to either
wrap MPI binaries installed through Julia's package manager or to make use of an existing MPI
installation.  Most Julia projects focusing on distributed-memory simulations seem to be using
MPI.jl, such as ClimateMachine.jl\footnote{\url{https://github.com/CliMA/ClimateMachine.jl}} or
ImplicitGlobalGrid.jl\footnote{\url{https://github.com/eth-cscs/ImplicitGlobalGrid.jl}}.  In
general, the performance of MPI programs written in Julia is comparable to C programs
\cite{hunold2020benchmarking}, and parallel simulations with Julia have been shown to scale
to more than 5{,}000 GPUs with MPI.jl \cite{omlin2020solving}.

@@

Even though the aforementioned difficulties do not prevent massively parallel simulations with
Julia, they raise the entry barrier for new users and developers. The overarching issue, however, is
that at the time of writing, there is little precedence in terms of openly available tutorials,
citable publications, or highly scalable example applications that can be used to learn about best
practices for MPI-based parallism in Julia. Thus, while in general it is justified to be cautiously
optimistic that most issues can be overcome, it is too early to make a final assessment on the
suitability of Julia for highly parallel simulations.

@@

Learning a new programming language naturally requires some time and effort.
In our experience, however, it has paid off and we do not want to miss the
many useful features of \trixi enabled by Julia and its ecosystem. While there is
no need to switch to Julia if people are satisfied with their existing
tools, we encourage researchers to try out Julia for scientific computing and to stay for a while.
The Julia
community (on the Julia Discourse forum\footnote{\url{https://discourse.julialang.org}}
or Slack/Zulip workspaces) is usually welcoming and helpful, both for new and
experienced users.
